Next Trippy Structures\thanks{Supported by organization x.}

### 2018-12-13 paper.tex
Pseudocode for queries

\usepackage{enumerate}
\usepackage{marginnote}

@@

All boring style except for \texttt{initialTimes}, which is compressed with sampled ZSTD.

\subsection{Matrices}
Tirso please explain what you did. Did you use bitmaps for partial sums? Matrices? Any other trick from inverted lists? Also explain how queries are solved again, in detail.

\subsection{CSA++}
A user trip can be represented by the stops where the user gets on the transportation system, so from now on we will consider a trip as a sequence of triplets $<s,l,j>$, where $s$, $l$ are, respectively, stop and line identifiers, while $j$ are the journey codes corresponding to the journeys that compose the trip. Additionally, as we are interested in knowing where the trips end, we also represent the last stop where the user got off, which line and journey will logically match the line and journey of the last get-on stop. Although it is generally hard to obtain information about the last destination stop of a trip, many transportation companies are investing effort in providing it, either by implementing systems to keep track of users as they leave their system or estimating it based on previous trips made by that user\marginnote{[CITATION NEEDED]}.

@@

>>>>

\usepackage{enumerate}
\usepackage[linesnumbered,commentsnumbered,boxed]{algorithm2e}
\usepackage{marginnote}

\newcommand{\acumm}{T-Matrices} % T is for Tirso!
\newcommand{\ctr}{NewCTR (name subject to change)}

@@

All of them stored explicitly except for $initialTime$, which is compressed with sampled ZSTD.

\subsection{\acumm}
Tirso please explain what you did. Did you use bitmaps for partial sums? Matrices? Any other trick from inverted lists? Also explain how queries are solved again, in detail.

\subsection{\ctr}
A user trip can be represented by the stops where the user gets on the transportation system, so from now on we will consider a trip as a sequence of triplets $<s,l,j>$, where $s$, $l$ are, respectively, stop and line identifiers, while $j$ are the journey codes corresponding to the journeys that compose the trip. Additionally, as we are interested in knowing where the trips end, we also represent the last stop where the user got off, which line and journey will logically match the line and journey of the last get-on stop. Although it is generally hard to obtain information about the last destination stop of a trip, many transportation companies are investing effort in providing it, either by implementing systems to keep track of users as they leave their system or estimating it based on previous trips made by that user\marginnote{[CITATION NEEDED]}.

@@

\begin{algorithm}[H]
\SetKwData{la}{l$_a$}\SetKwData{lz}{l$_z$}\SetKwData{sa}{s$_a$}\SetKwData{sz}{s$_z$}\SetKwData{ta}{t$_a$}\SetKwData{tz}{t$_z$}\SetKwData{pattern}{pattern}\SetKwData{left}{left}\SetKwData{right}{right}\SetKwData{csa}{CSA}\SetKwData{wmj}{WMJ}\SetKwData{leftzero}{left$_0$}\SetKwData{rightzero}{right$_0$}\SetKwData{a}{a}\SetKwData{z}{z}\SetKwData{ja}{j$_a$}\SetKwData{jz}{j$_z$}\SetKwData{n}{n}\SetKwData{ap}{a'}\SetKwData{zp}{z'}\SetKwData{offset}{offset}
 \SetKwFunction{GetRange}{GetRange}\SetKwFunction{GetJCodes}{GetJCodes}\SetKwFunction{GetCount}{GetCount}\SetKwFunction{GetPsi}{$\Psi$}\SetKwFunction{GetRangeSpecial}{GetRange$^*$}\SetKwFunction{wml}{WML}\SetKwFunction{TrackUp}{TrackUp}\SetKwFunction{Select}{Select}
 \KwData{\la,\lz,\sa,\sz, times \ta,\tz and length of the sequence \n}
 \KwResult{Number of occurences}
 \BlankLine
 \pattern $\leftarrow \{\sz,0,\sa\}$\;
 \left,\right $\leftarrow$ \GetRange{\csa, $0$, \n, \pattern}\;
 \leftzero $\leftarrow$ \GetPsi{\csa, \left}\;
 \rightzero $\leftarrow$ \GetPsi{\csa, \right}\;
 \tcp{\right-\left = \rightzero-\leftzero}
 \a,\z $\leftarrow$ \GetRange{\wml{0},\leftzero,\rightzero,\la}\;
 \ja,\jz $\leftarrow$ \GetJCodes{\la,\sa,\ta,\tz}\;
 \a,\z $\leftarrow$ \GetRangeSpecial{\wmj,\a,\z,\ja,\jz}\;
 \ap $\leftarrow$ \TrackUp{\wml{0},\a}\;
 \zp $\leftarrow$ \TrackUp{\wml{0},\z}\;
 \tcp{\z-\a = \zp-\ap}
 \offset $\leftarrow$ \Select{\csa,\sz}\;
 \a,\z $\leftarrow$ \GetRange{\wml{\sz},\left-\offset~$+$~\ap-\leftzero,
 \left-\offset~$+$~\ap-\leftzero,\lz}\;
 \ja,\jz $\leftarrow$ \GetJCodes{\lz,\sz,\ta,\tz}\;
 \Return{\GetCount{\wmj,\offset~+~\a,\offset~+~\z,\ja,\jz}}\;

 \caption{Querying for all features on \ctr}
\end{algorithm}
